### 2018-05-30 Sections/QTCP_protocol_stack.tex
CV figs, sec
Figure reformatting to make double column, rather than stacked

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function Transport(Packet):
\begin{enumerate}
    \item nextNode = Packet.RoutingQueue.Pop()
    \item Packet.PhysicallySendTo(nextNode)
    \item Packet.WaitUntilArrivesAt(nextNode)
    \item checksum = Hash(Packet.Header + Packet.ClassicalData)
    \item if(checksum $\neq$ Packet.Header.Checksum) \{
    \setlength{\itemindent}{0.2in}
    \item Packet.Sender.Notify(\textsc{Failure})
    \item Packet.Recipient.Notify(\textsc{Failure})
    \item Packet.Discard()
    \item $\Box$
        \setlength{\itemindent}{0in}
\item \}
    \item Packet.Costs += IncomingLink.Costs
    \item Packet.Attributes.Update()
    \item if(Packet.RoutingQueue.Length = 0) \{
    \setlength{\itemindent}{0.2in}
    \item Return(Packet)
        \setlength{\itemindent}{0in}
    \item \}
    \setlength{\itemindent}{0in}
    \item $\Box$
\end{enumerate}}}}
\caption{Algorithm implemented by the \textsc{Transport} layer of QTCP for each \textsc{Packet}. The \texttt{Attributes.Update()} function is left undefined. This is where arbitrary \textsc{Attribute} dynamics may take place.} \label{alg:transport_alg}
\end{table}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function Reconstruction(Packets):
\begin{enumerate}
    \item Packets.WaitUntilAllReceived()
    \item message = Packets.SortByOrderAscending().data
    \item Packets.Receiver.Notify(message)
     \item $\Box$
\end{enumerate}}}}
\caption{The goal of the \textsc{Reconstruction} layer, is to take a collection of received \textsc{Packets} and reassemble them into the \textsc{Message}.} \label{alg:reconstruction}
\end{table}

@@

\subsubsection{Quality of service (QoS)} \label{sec:QOS} \index{Quality of service (QoS) layer}

>>>>

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ \
function Transport(Packet):
\begin{enumerate}
    \item nextNode = Packet.RoutingQueue.Pop()
    \item Packet.PhysicallySendTo(nextNode)
    \item Packet.WaitUntilArrivesAt(nextNode)
    \item checksum = Hash(Packet.Header + Packet.ClassicalData)
    \item if(checksum $\neq$ Packet.Header.Checksum) \{
    \setlength{\itemindent}{0.2in}
    \item Packet.Sender.Notify(\textsc{Failure})
    \item Packet.Recipient.Notify(\textsc{Failure})
    \item Packet.Discard()
    \item $\Box$
        \setlength{\itemindent}{0in}
\item \}
    \item Packet.Costs += IncomingLink.Costs
    \item Packet.Attributes.Update()
    \item if(Packet.RoutingQueue.Length = 0) \{
    \setlength{\itemindent}{0.2in}
    \item Return(Packet)
        \setlength{\itemindent}{0in}
    \item \}
    \setlength{\itemindent}{0in}
    \item $\Box$
\end{enumerate}}}}
\caption{Algorithm implemented by the \textsc{Transport} layer of QTCP for each \textsc{Packet}. The \texttt{Attributes.Update()} function is left undefined. This is where arbitrary \textsc{Attribute} dynamics may take place.} \label{alg:transport_alg}
\end{table}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function Reconstruction(Packets):
\begin{enumerate}
    \item Packets.WaitUntilAllReceived()
    \item message = Packets.SortByOrderAscending().data
    \item Packets.Receiver.Notify(message)
     \item $\Box$
\end{enumerate}}}}
\caption{The goal of the \textsc{Reconstruction} layer, is to take a collection of received \textsc{Packets} and reassemble them into the \textsc{Message}. \comment{Not referenced in text!}} \label{alg:reconstruction}
\end{table}

@@

\subsubsection{Quality of service} \label{sec:QOS} \index{Quality of service layer}

### 2018-05-30 Sections/collision_handling_and_classical_errors.tex
Figure reformatting to make double column, rather than stacked

Alternately, Alice might be a part of a distributed computation, where she didn't prepare the data in the first place. In this instance, the no-cloning theorem implies that she cannot, in general, learn what the quantum state was, and therefore would be unable to make a second transmission attempt.

>>>>

Alternately, Alice might be a part of a distributed computation, where she didn't prepare the data in the first place. In this instance, the no-cloning theorem\index{No-cloning theorem}\footnote{The no-cloning theorem states that it is impossible to take a completely unknown quantum state and prepare an identical copy of it. That is, there is no quantum process implementing the map \mbox{$\mathcal{E}(\hat\rho\otimes\ket{0}\bra{0}) \to \hat\rho\otimes\hat\rho$} for unknown $\hat\rho$. Note that this result applies when $\hat\rho$ is arbitrary and unknown, but in general needn't apply if it is restricted to a particular basis, subject to other constraints, or we have a priori knowledge of the state.} implies that she cannot, in general, learn what the quantum state was, and therefore would be unable to make a second transmission attempt.

### 2018-05-30 Sections/economics_of_the_quantum_internet.tex
Figure reformatting to make double column, rather than stacked

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{cost_of_comp_n} \\
\includegraphics[width=0.4\textwidth]{cost_of_comp_n2} \\
\includegraphics[width=0.4\textwidth]{cost_of_comp_2n}
\caption{Examples of the temporal dynamics of the cost of computation for different scaling functions and exponential growth rates. Units are \mbox{$C_0=N_0=n=1$}, with RoR \mbox{$\gamma_\text{ror}=0$}. A non-zero RoR would simply scale these figures by a constant factor of $e^{\gamma_\text{ror}}$.}\label{fig:econ_cost_of_comp}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.42\textwidth]{single_qubit_QCL}
\caption{Time-dependent quantum computational leverage for a single qubit (\mbox{$n=1$}) with different computational scaling functions, under the assumption of exponential network growth in units of \mbox{$N_0=1$}.}\label{fig:time_dep_QCL}
\end{figure}

@@

Note that in the limit of \mbox{$T\to 0$} this reduces to the spot price of the asset. That is,
\begin{align}
	F(0)=L(0),
\end{align}
as expected.

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{forward_cont_pricing_mod_1}\\
\includegraphics[width=0.4\textwidth]{forward_cont_pricing_mod_2}
\caption{Forward price on a computation to be delivered at time $T$ in the future, in units \mbox{$C_0=N_0=1$}, where we are assuming an exponential scaling function, \mbox{$f_\text{sc}(n)=e^n$}.}\label{fig:forward_cont_pricing_mod}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{tax_exp} \\
\includegraphics[width=0.47\textwidth]{tax_subsidy}
\caption{(top) Relationship between the tax performance multiplier, (positive) tax rate, and network size, assuming an exponential computational scaling function, in the regime of positive taxation, \mbox{$\gamma_T>1$}. (bottom) For \mbox{$N_\text{tax}=10$}, a zoom into the region around neutral taxation, where \mbox{$\gamma_T\approx 1$}, showing slight degrees of both taxation (\mbox{$\gamma_T>1$}) and subsidisation (\mbox{$\gamma_T<1$}). Neutral taxation, \mbox{$\gamma_T=1$}, is shown in orange.}\label{fig:tax_exp}\index{Tea party}\index{Don't tread on me}
\end{figure}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function QuantCoin($\hat{U}_\text{comp}$, blockchain, data, reward):
\begin{enumerate}
	\item Alice homomorphically/blindly encrypts $data$,
		\begin{align}
			encryptedInput = homoEncrypt(data)
		\end{align}
	\item Alice commits the $encryptedInput$ to the public $blockchain$,
	\begin{align}
	blockchain.commit(encryptedInput)	
	\end{align}
	\item Alice places into escrow Bob's $reward$,
	\begin{align}
		escrow.hold(reward)
	\end{align}
	\item Bob processes the $encryptedInput$ using $\hat{U}_\text{comp}$,
	\begin{align}
		encryptedOutput = \hat{U}_\text{comp}(encryptedInput)
	\end{align}
	\item Bob commits encrypted output to the $blockchain$,
	\begin{align}
	blockchain.commit(encryptedOutput)	
	\end{align}
	\item Alice and Bob execute a verification protocol,
	\begin{align}
	proof = verify(encryptedOutput)	
	\end{align}
	\item The $proof$ is committed to the $blockchain$ (as is every step of the proof if it is an interactive one),
	\begin{align}
		blockchain.commit(proof)
	\end{align}
	\item The $blockchain$ network inspects that the verification is valid.
	\item If valid, the $blockchain$ hashes the data and proof, encapsulating it into a QuantCoin\texttrademark\,token, which is given to Bob,
	\begin{align}
		&token = \text{SHA256}(encryptedInput\nonumber\\
		&+ encryptedOutput + proof)\nonumber\\
		&Bob.receive(token)
	\end{align}
	\item The $reward$ held in escrow is released to Bob,
	\begin{align}
		escrow.release(Bob)
	\end{align}
\end{enumerate}}}}
\caption{Sketch for how a quantum computation-backed cryptocurrency might be implemented. We have abstracted away the underlying Blockchain protocol, interfacing with it using a high-level API, since Blockchain technology is highly liable to evolve. We similarly call upon verification subroutines using a high-level implementation-independent API.} \label{alg:quant_coin}
\end{table}

@@

\renewcommand{\tablename}{TABLE}
\renewcommand{\arraystretch}{0.5}

@@

\renewcommand{\arraystretch}{1}
\renewcommand{\tablename}{ALG.}

>>>>

\begin{figure*}[!htb]
\includegraphics[width=0.325\textwidth]{cost_of_comp_n}
\includegraphics[width=0.325\textwidth]{cost_of_comp_n2}
\includegraphics[width=0.325\textwidth]{cost_of_comp_2n}
\caption{Examples of the temporal dynamics of the cost of computation for different scaling functions and exponential growth rates. Units are \mbox{$C_0=N_0=n=1$}, with RoR \mbox{$\gamma_\text{ror}=0$}. A non-zero RoR would simply scale these figures by a constant factor of $e^{\gamma_\text{ror}}$.}\label{fig:econ_cost_of_comp}
\end{figure*}

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{single_qubit_QCL}
\caption{Time-dependent quantum computational leverage for a single qubit (\mbox{$n=1$}) with different computational scaling functions, under the assumption of exponential network growth in units of \mbox{$N_0=1$}.}\label{fig:time_dep_QCL}
\end{figure}

@@

Note that in the limit of \mbox{$T\to 0$} this reduces to the spot price of the asset,
\begin{align}
	F(0)=L(0),
\end{align}
as expected.

\begin{figure*}[!htb]
\includegraphics[width=0.47\textwidth]{forward_cont_pricing_mod_1}
\includegraphics[width=0.47\textwidth]{forward_cont_pricing_mod_2}
\caption{Forward price on a computation to be delivered at time $T$ in the future, in units \mbox{$C_0=N_0=1$}, where we are assuming an exponential scaling function, \mbox{$f_\text{sc}(n)=e^n$}.}\label{fig:forward_cont_pricing_mod}
\end{figure*}

@@

\begin{figure*}[!htb]
\includegraphics[width=0.47\textwidth]{tax_exp}
\includegraphics[width=0.47\textwidth]{tax_subsidy}
\caption{(top) Relationship between the tax performance multiplier, (positive) tax rate, and network size, assuming an exponential computational scaling function, in the regime of positive taxation, \mbox{$\gamma_T>1$}. (bottom) For \mbox{$N_\text{tax}=10$}, a zoom into the region around neutral taxation, where \mbox{$\gamma_T\approx 1$}, showing slight degrees of both taxation (\mbox{$\gamma_T>1$}) and subsidisation (\mbox{$\gamma_T<1$}). Neutral taxation, \mbox{$\gamma_T=1$}, is shown in orange.}\label{fig:tax_exp}\index{Tea party}\index{Don't tread on me}
\end{figure*}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function QuantCoin($\hat{U}_\text{comp}$, blockchain, data, reward):
\begin{enumerate}
	\item Alice homomorphically/blindly encrypts $data$,
		\begin{align}
			encryptedInput = homoEncrypt(data)
		\end{align}
	\item Alice commits the $encryptedInput$ to the public $blockchain$,
	\begin{align}
	blockchain.commit(encryptedInput)	
	\end{align}
	\item Alice places into escrow Bob's $reward$,
	\begin{align}
		escrow.hold(reward)
	\end{align}
	\item Bob processes the $encryptedInput$ using $\hat{U}_\text{comp}$,
	\begin{align}
		encryptedOutput = \hat{U}_\text{comp}(encryptedInput)
	\end{align}
	\item Bob commits encrypted output to the $blockchain$,
	\begin{align}
	blockchain.commit(encryptedOutput)	
	\end{align}
	\item Alice and Bob execute a verification protocol,
	\begin{align}
	proof = verify(encryptedOutput)	
	\end{align}
	\item The $proof$ is committed to the $blockchain$ (as is every step of the proof if it is an interactive one),
	\begin{align}
		blockchain.commit(proof)
	\end{align}
	\item The $blockchain$ network inspects that the verification is valid.
	\item If valid, the $blockchain$ hashes and signs the data and proof, encapsulating it into a QuantCoin\texttrademark\,token, which is given to Bob,
	\begin{align}
		&token = \text{SHA256}(encryptedInput\nonumber\\
		&+ encryptedOutput + proof)\nonumber\\
		&token.sign(blockchain)\nonumber\\
		&Bob.receive(token)
	\end{align}
	\item The $reward$ held in escrow is released to Bob,
	\begin{align}
		escrow.release(Bob)
	\end{align}
\end{enumerate}}}}
\caption{Sketch for how a quantum computation-backed cryptocurrency might be implemented. We have abstracted away the underlying Blockchain protocol, interfacing with it using a high-level API, since Blockchain technology is highly liable to evolve. We similarly call upon verification subroutines using a high-level implementation-independent API.} \label{alg:quant_coin}
\end{table}

@@

\startnormtable
\renewcommand{\arraystretch}{0.5}

@@

\renewcommand{\arraystretch}{1}
\startalgtable
